Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-08-20 ms.tex
Writing J0 as a sum over spatial modes
fixing Jd

\be
J_{\rm d} & = & 
\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (k/\Delta)^2\left[ (x-x_{\rm s})^2 + (y-y_{\rm s})^2 + (z-z_{\rm s})^2 \right] + (\sigma - \sigma_{\rm s})^2}.
\label{eq:Jd}
\ee

@@

A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}. They found a solution which satisfies a $J=0$ boundary condition at $r=R$. We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center. The result is
\be
J_0 & = & \left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
\left( \frac{1}{Rr} \right)
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right)
\label{eq:J0}
\ee

@@

We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ over-plotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$. The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result. Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.

>>>>

\be
J_{\rm d} & = & 
\frac{(\sqrt{6}k^2L)/(16\pi^3 \Delta^3)}{ (kr/\Delta)^2 + (\sigma - \sigma_{\rm s})^2}.
\label{eq:Jd}
\ee

@@

A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}. They found a solution which satisfies a $J=0$ boundary condition at $r=R$. We generalize their solution to allow emission at frequency $\nu_{\rm s}$ away from line center. The result can be written as a sum over spatial modes,
\be
J_0 = \frac{\sqrt{6}}{16\pi} \frac{L}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
\ee
which evaluates to
\be
J_0 & = & \left( \frac{\sqrt{6}L}{32\pi^2 \Delta} \right)
\left( \frac{1}{Rr} \right)
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right)
\label{eq:J0}
\ee

@@

We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo escape probability as a function of frequency is shown with that of the solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$. The escape probability $P(x)$ is defined as the total luminosity at the surface divided by the source luminosity, or
\be
P(x) = \frac{16\pi^2R^2H(x)}{L}
\ee
The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result. Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.
